Approximation as Differentiation

### 2025-05-05 main/formal-structures.tex
Tweaks.

Happily, $\FinVect$ and $\LatGal$ both have biproducts, as a consequence of them having products and being enriched in commutative monoids\todo{fwd ref}. However, neither of them have all small products, without moving to infinite dimensional vector spaces (in the case of $\FinVect$) or complete lattices (in the case of $\LatGal$). Neither of these are ideal. In infinite dimensional vector spaces, dualisation is not involutive and the connection between the forward and reverse derivatives is lost. In complete lattices, we can no longer easily implement the infinite meets and joins required, and we lose the computability of the model. Moreover, in Agda, there are issues with predicativity when considering complete lattices.\todo{be more specific}

Vákár overcomes this by using different interpretations for forward and backward derivatives. we overcome this by using Cmon-enriched presheaves.\todo{elaborate.}

>>>>

Happily, $\FinVect$ and $\LatGal$ both have biproducts, as a consequence of them having products and being enriched in commutative monoids\todo{fwd ref}. However, neither of them has all small products, without moving to infinite dimensional vector spaces (in the case of $\FinVect$) or complete lattices (in the case of $\LatGal$). Neither of these are ideal. In infinite dimensional vector spaces, dualisation is not involutive and the connection between the forward and reverse derivatives is lost. In complete lattices, we can no longer easily implement the infinite meets and joins required, and we lose the computability of the model. Moreover, in Agda, there are issues with predicativity when considering complete lattices.\todo{be more specific}

Vákár overcomes this by using different interpretations for forward and backward derivatives. we overcome this by using $\CMon$-enriched presheaves.\todo{elaborate.}
